\documentclass[10pt,a4paper]{article}

% --- 패키지 로드 ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{verbatim}

% --- 전체 줄 간격 ---
\linespread{1.1}

% --- URL 스타일 ---
\hypersetup{colorlinks=true, urlcolor=blue}

% --- 섹션 스타일 ---
\titleformat{\section}{
  \vspace{0pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% --- [간격 및 여백 최적화] 리스트 설정 ---
\setlist[itemize]{
    itemsep=6pt,      % 항목(itemize 내의 \item) 간의 기본 간격
    parsep=0pt,
    topsep=0pt,
    partopsep=0pt,
    leftmargin=0.15in, 
    rightmargin=0pt,
    label={},
    labelsep=0pt
}

% --- [명령어 재정의] 수동 vspace 제거를 위한 최적화 ---

\newcommand{\resumeItemList}[1]{
  \item[] \leavevmode 
  \begin{tabular*}{\linewidth}{@{}l@{}}
     {#1} \\
  \end{tabular*}\vspace{-5pt}
}

% 1. 헤딩 명령어: 하단 여백을 내부적으로 조정
\newcommand{\resumeHeading}[2]{
  \item[] \leavevmode \normalsize
  \begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & #2 \\
  \end{tabular*}\vspace{-5pt} 
}

\newcommand{\resumeCourse}[1]{
  \item[] \leavevmode \small
  \begin{tabular*}{\linewidth}{@{}l@{}}
    {#1} \\
  \end{tabular*}\vspace{-5pt}
}

% 2. 하부 상세 항목: 들여쓰기를 유지하며 하단 여백 조정
% --- [수정된 명령어] 헤딩보다 안쪽으로 들여쓰기 + 줄바꿈 정렬 유지 ---
\newcommand{\resumeSubItem}[1]{
  \item[] 
  \begin{itemize}[leftmargin=0.15in, label={}, nosep]
    \item \small{#1}
  \end{itemize}
  \vspace{-5pt} % 항목 간 간격 조절
}

\newcommand{\resumePublication}[1]{
  \item[] \small{#1} \vspace{-5pt}
}

\begin{document}

% --- 헤더 ---
\begin{center}
    {\Huge  \textbf{SUNGJAE AHN}} \\ \vspace{6pt}
    \small 
    \href{mailto:danielahn010@khu.ac.kr}{danielahn010@khu.ac.kr} $|$ 
    \href{https://github.com/dmach1ne}{github} $|$
    \href{https://dmach1ne.github.io}{webpage}
    \vspace{4pt}
\end{center}
% --- Research Interest ---
\section{Research Interest}
\begin{itemize}
    \item[] \small 
    I believe that achieving Artificial General Intelligence (AGI) requires learning paradigms that enable agents to adapt and improve through \href{https://storage.googleapis.com/deepmind-media/Era-of-Experience%20/The%20Era%20of%20Experience%20Paper.pdf}{autonomous experience}, much like \textbf{Reinforcement Learning}. 
    In this context, my primary research interest lies in \textbf{\href{https://arxiv.org/pdf/1912.05500}{meta-learning intrinsic reward}} functions that generalize across diverse environments, enabling agents to rapidly adapt to unseen tasks.
\end{itemize}

% --- Education ---
\section{Education}
\begin{itemize}
    \resumeHeading{Kyung Hee University (KHU)}{Expected Graduation: Feb. 2027}
    \resumeSubItem{{B.S. in Computer Science and Engineering}}
    \vspace{-2pt}
    \resumeSubItem{GPA : 4.05/4.3 (4.29/4.5)}
\end{itemize}

% --- Experience ---
\section{Research Experience}
\begin{itemize}
    \resumeHeading{\href{https://airlab.khu.ac.kr/publication/}{AI \& Robotics Lab (AIR Lab)}, KHU}{Dec. 2025 -- Present}
    \item[] \small Undergraduate Researcher (Advisor: Prof. Hyoseok Hwang)
    \vspace{-5pt}
    \resumeSubItem{\textbullet \
    Demonstrated that temporal penalties induce spatial smoothness through off-policy transitions, eliminating the need for explicit spatial penalties.
    }
    \resumeSubItem{\textbullet \
    Investigating self-distillation approach for preserving reasoning diversity of Large Language Models.
    }
\end{itemize}

\section{Projects}
\begin{itemize}
    \resumeHeading{Enhanced \href{https://arxiv.org/abs/2601.20802}{Self-Distillation Policy Optimization}}{Spring 2026 -- Present}
    \resumeSubItem{\textbullet \
    Exploring maximum entropy regularization to expanded Top-K tokens to enhance exploration of the student.
    }
\end{itemize}
\vspace{5pt}
\begin{itemize}
    \resumeHeading{\href{https://aifactory.space/task/9197/leaderboard}{Deepfake Detection Competition} (Held by NFS)}{Fall 2025}
\resumeSubItem{\textbullet \ Ranked 33 out of 266 teams utilizing Dual Data Alignment for robust cross-domain forgery detection.}
\resumeSubItem{\textbullet \ Leveraged Hydra and WandB to manage experimental configurations and ensure research reproducibility.}
\vspace{-2pt}
\end{itemize}

% --- Activities ---
\section{Activities}
\begin{itemize}
    \resumeHeading{CSE 304 Algorithms}{Spring, Fall 2025}
    \resumeSubItem{SW-mentor at KHU}
    \resumeHeading{KHUDA (KHU Data analysis and AI club) 7th}{Jan. 2025 - Jul. 2025}
    \resumeSubItem{NLP Track, Developed RAG-based Chatbot}
    \resumeHeading{\textnormal{Signal Intelligence}}{Feb. 2022 - Nov. 2023}
    \resumeSubItem{Mandatory Military Service}
\end{itemize}

% --- Skills ---
\section{Skills}
\begin{itemize}[itemsep=2pt]
    \resumeHeading{AI/ML : \textnormal{\small PyTorch, Gymnasium, Slurm}}{}
    \vspace{-10pt}
    \resumeHeading{English : \textnormal{\small TOEIC 970}}{}
\end{itemize}

% --- Awards ---
\section{Awards}
\begin{itemize}
    \resumeHeading{Academic Excellence Scholarship, \textnormal{KHU}}{Fall 2025}
    \resumeHeading{Academic Excellence Scholarship, \textnormal{KHU}}{Spring 2025}
    \resumeHeading{Academic Excellence Scholarship, \textnormal{KHU}}{Fall 2024}
    \resumeHeading{Academic Excellence Scholarship, \textnormal{KHU}}{Spring 2024}
\end{itemize}

\begin{comment}
% --- Related Courses: 다른 항목들과 들여쓰기 통일 ---
\section{RELATED COURSES}
\begin{itemize}
    \resumeCourse{Deep Learning, Machine Learning in Practice, Operation Research II, Big Data Mining, AI Programming}
\end{itemize}
\end{comment}

\end{document}